Measuring variation in gaze following across communities, ages, and individuals --- a showcase of the TANGO--CC

### 2024-06-19 paper/manuscript.tex
upload preprint

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{cross-cultural psychology, social cognition, gaze following, individual differences, reliability\newline\indent Word count: 5457}
\usepackage{lineno}

@@

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Measuring variation in gaze following across communities, ages, and individuals --- a showcase of the TANGO--CC},
  pdfauthor={Julia Christin Prein (ORCID: 0000-0002-3154-6167)1,2, Florian M. Bednarski (ORCID: 0000-0003-4384-4791)4, Ardain Dzabatou5, Michael C. Frank (ORCID: 0000-0002-7551-4378)6, Annette M. E. Henderson (ORCID: 0000-0003-4384-4791)4, Josefine Kalbitz2, Patricia Kanngiesser (ORCID:0000-0003-1068-3725)7, Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733)8, Bahar Köymen (ORCID: 0000-0001-5126-8240)9, Maira V. Manrique-Hernandez2, Shirley Magazi (ORCID: 0009-0006-0479-9800)10, Lizbeth Mújica-Manrique2, Julia Ohlendorf2, Damilola Olaoba2, Wesley R. Pieters (ORCID:0000-0002-6152-249X)10, Sarah Pope-Caldwell2, Umay Sen (ORCID: 0000-0001-9488-0851)13, Katie Slocombe (ORCID: 0000-0002-7310-1887)11, Robert Z. Sparks (ORCID: 0000-0001-7545-0522)6, Roman Stengelin (ORCID: 0000-0003-2212-4613)2,10, Jahnavi Sunderarajan2, Kirsten Sutherland2, Florence Tusiime3, Wilson Vieira (ORCID: 0009-0001-9400-6328)2, Zhen Zhang (ORCID: 0000-0001-9300-0920)12, Yufei Zong (ORCID: 0009-0000-5012-0244)12, Daniel B. M. Haun (ORCID: 0000-0002-3262-645X)2,+, \& Manuel Bohn (ORCID: 0000-0001-6006-1348)1,2,+},
  pdflang={en-EN},
  pdfkeywords={cross-cultural psychology, social cognition, gaze following, individual differences, reliability},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Measuring variation in gaze following across communities, ages, and individuals --- a showcase of the TANGO--CC}
\author{Julia Christin Prein (ORCID: 0000-0002-3154-6167)\textsuperscript{1,2}, Florian M. Bednarski (ORCID: 0000-0003-4384-4791)\textsuperscript{4}, Ardain Dzabatou\textsuperscript{5}, Michael C. Frank (ORCID: 0000-0002-7551-4378)\textsuperscript{6}, Annette M. E. Henderson (ORCID: 0000-0003-4384-4791)\textsuperscript{4}, Josefine Kalbitz\textsuperscript{2}, Patricia Kanngiesser (ORCID:0000-0003-1068-3725)\textsuperscript{7}, Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733)\textsuperscript{8}, Bahar Köymen (ORCID: 0000-0001-5126-8240)\textsuperscript{9}, Maira V. Manrique-Hernandez\textsuperscript{2}, Shirley Magazi (ORCID: 0009-0006-0479-9800)\textsuperscript{10}, Lizbeth Mújica-Manrique\textsuperscript{2}, Julia Ohlendorf\textsuperscript{2}, Damilola Olaoba\textsuperscript{2}, Wesley R. Pieters (ORCID:0000-0002-6152-249X)\textsuperscript{10}, Sarah Pope-Caldwell\textsuperscript{2}, Umay Sen (ORCID: 0000-0001-9488-0851)\textsuperscript{13}, Katie Slocombe (ORCID: 0000-0002-7310-1887)\textsuperscript{11}, Robert Z. Sparks (ORCID: 0000-0001-7545-0522)\textsuperscript{6}, Roman Stengelin (ORCID: 0000-0003-2212-4613)\textsuperscript{2,10}, Jahnavi Sunderarajan\textsuperscript{2}, Kirsten Sutherland\textsuperscript{2}, Florence Tusiime\textsuperscript{3}, Wilson Vieira (ORCID: 0009-0001-9400-6328)\textsuperscript{2}, Zhen Zhang (ORCID: 0000-0001-9300-0920)\textsuperscript{12}, Yufei Zong (ORCID: 0009-0000-5012-0244)\textsuperscript{12}, Daniel B. M. Haun (ORCID: 0000-0002-3262-645X)\textsuperscript{2,+}, \& Manuel Bohn (ORCID: 0000-0001-6006-1348)\textsuperscript{1,2,+}}
\date{}

@@

The authors made the following contributions. Julia Christin Prein (ORCID: 0000-0002-3154-6167): Conceptualization, Methodology, Software, Formal Analysis, Resources, Writing - Original Draft Preparation, Writing - Review \& Editing; Florian M. Bednarski (ORCID: 0000-0003-4384-4791): Resources, Writing - Review \& Editing; Ardain Dzabatou: Resources, Writing - Review \& Editing; Michael C. Frank (ORCID: 0000-0002-7551-4378): Resources, Writing - Review \& Editing; Annette M. E. Henderson (ORCID: 0000-0003-4384-4791): Resources, Writing - Review \& Editing; Josefine Kalbitz: Resources, Writing - Review \& Editing; Patricia Kanngiesser (ORCID:0000-0003-1068-3725): Resources, Writing - Review \& Editing; Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733): Resources, Writing - Review \& Editing; Bahar Köymen (ORCID: 0000-0001-5126-8240): Resources, Writing - Review \& Editing; Maira V. Manrique-Hernandez: Resources, Writing - Review \& Editing; Shirley Magazi (ORCID: 0009-0006-0479-9800): Resources, Writing - Review \& Editing; Lizbeth Mújica-Manrique: Resources, Writing - Review \& Editing; Julia Ohlendorf: Resources, Writing - Review \& Editing; Damilola Olaoba: Resources, Writing - Review \& Editing; Wesley R. Pieters (ORCID:0000-0002-6152-249X): Resources, Writing - Review \& Editing; Sarah Pope-Caldwell: Resources, Writing - Review \& Editing; Umay Sen (ORCID: 0000-0001-9488-0851): Resources, Writing - Review \& Editing; Katie Slocombe (ORCID: 0000-0002-7310-1887): Resources, Writing - Review \& Editing; Robert Z. Sparks (ORCID: 0000-0001-7545-0522): Resources, Writing - Review \& Editing; Roman Stengelin (ORCID: 0000-0003-2212-4613): Resources, Writing - Review \& Editing; Jahnavi Sunderarajan: Resources, Writing - Review \& Editing; Kirsten Sutherland: Resources, Writing - Review \& Editing; Florence Tusiime: Resources, Writing - Review \& Editing; Wilson Vieira (ORCID: 0009-0001-9400-6328): Resources, Writing - Review \& Editing; Zhen Zhang (ORCID: 0000-0001-9300-0920): Resources, Writing - Review \& Editing; Yufei Zong (ORCID: 0009-0000-5012-0244): Resources, Writing - Review \& Editing; Daniel B. M. Haun (ORCID: 0000-0002-3262-645X): Funding acquisition, Writing - Review \& Editing; Manuel Bohn (ORCID: 0000-0001-6006-1348): Conceptualization, Methodology, Writing - Review \& Editing.

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute of Psychology in Education, Leuphana University Lüneburg, Germany\\\textsuperscript{2} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Germany\\\textsuperscript{3} Budongo Conservation Field Station, Uganda\\\textsuperscript{4} School of Psychology, University of Auckland, New Zealand\\\textsuperscript{5} Université Marien Ngouabi, Republic of the Congo\\\textsuperscript{6} Department of Psychology, Stanford University, USA\\\textsuperscript{7} School of Psychology, University of Plymouth, UK\\\textsuperscript{8} Department of Psychology, Koç University, Türkiye\\\textsuperscript{9} Division of Psychology, Communication, and Human Neuroscience, University of Manchester, UK\\\textsuperscript{10} Department of Psychology and Social Work, University of Namibia, Namibia\\\textsuperscript{11} Department of Psychology, University of York, UK\\\textsuperscript{12} CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences, China\\\textsuperscript{13} Department of Psychology, Developmental Psychology, Uppsala University, Sweden\\\textsuperscript{+} joint last author}

\abstract{%
Cross-cultural studies are crucial for investigating cultural variability and universality of cognitive developmental processes. However, cross-cultural assessment tools in cognition across languages and communities are limited. This paper describes a gaze following task designed to measure basic social cognition across individuals, ages, and communities (Task for Assessing iNdividual Differences in Gaze understanding Open -- Cross-Cultural or TANGO--CC). The TANGO--CC was developed and psychometrically assessed in one cultural setting and, with the input of local collaborators, adapted for cross-cultural data collection. Minimal language demands and the web-app implementation allow fast and easy contextual adaptations to each community. The TANGO--CC captures individual- and community-level variation and shows good internal consistency in a data set from 2.5- to 11-year-old children from 17 diverse communities. Within-community variation outweighed between-community variation. We provide an open-source website for researchers to customize and use the task. The TANGO--CC can be used to assess basic social cognition in diverse communities and provides a roadmap for researching community-level and individual-level differences across cultures.
}

@@

For decades, researchers have advocated for more diverse samples in psychological research and cautioned against relying solely on convenience samples from the Global North (Arnett, 2008; Henrich et al., 2010; Lillard, 1998).
Despite numerous calls for change, the samples reported in major psychology journals still lack diversity (Apicella et al., 2020; Gutchess \& Rajaram, 2023; Thalmayer et al., 2021).
This hinders progress in theory building and testing: we cannot draw inferences about universal and variable aspects of the human cognitive system from data collected exclusively in one single communities (Krys et al., 2024).
While this sampling bias is often discussed within adult psychology, it is equally relevant for developmental psychology (Nielsen et al., 2017).
Early experiences shape the way children think about and interact with the world and an ontogenetic perspective is needed to explore the foundational aspects of human behavioral diversity (Amir \& McAuliffe, 2020; Broesch et al., 2023; Liebal \& Haun, 2018; Torréns et al., 2023).

There are numerous challenges with collecting cross-cultural, developmental data (Amir \& McAuliffe, 2020; Broesch et al., 2023).
Cross-cultural studies need reliable and valid measures to systematically capture variation between communities and/or individuals.
However, studies on social cognition with US-American and European samples rarely report psychometric information (for a review, see Beaudoin et al., 2020), and the picture further deteriorates when we look at cross-cultural social cognition tasks (Bourdage et al., 2023; Hajdúk et al., 2020; Waschl \& Chen, 2022).
Thus, it is already challenging to find reliable and valid tasks that have measurement sensitivity to detect individual differences within one community, let alone tasks that do so across different communities.
In this paper, we describe the construction and psychometric evaluation of a cross-cultural measure of basic social cognition (gaze following) in children as a concrete example for how to address this problem.

Adapting tasks to diverse communities and assessing their validity and reliability might be especially important in the social-cognitive domain.
Social cognition refers to how an individual processes information in social situations which allows them to understand and predict others' behavior (Adolphs, 1999; Decety, 2020; Frith \& Frith, 2007; Zeigler-Hill et al., 2015).
If, in theory, stimuli used in social cognition tasks should relate to people's everyday experiences, then tasks themselves should be tuned to the features of specific communities.
Indeed, task performance can be diminished when stimuli do not reflect characteristics of the participants' communities (Peña, 2007).
For example, Elfenbein and Ambady (2002) found better emotion recognition for members of the same national, ethnic, or regional group.
Selcuk et al. (2023) concluded that children often attribute mental states more accurately and more frequently to individuals from the same community.

There exists a continuum of approaches that researchers can take to collect cross-cultural data, and the decision for a specific method partly depends on whether researchers aim to increasing the \emph{depth} (culture specificity) or \emph{breadth} (standardization across multiple communities) of our psychological knowledge (Amir \& McAuliffe, 2020).
At one extreme, researchers translate the psychological construct into an individually designed study for each community (termed ``assembly''; He and Vijver (2012), Waschl and Chen (2022)).
While this approach allows greater flexibility and sensitivity to cultural differences, it might not be feasible for studying a multitude of communities as it becomes too demanding and time-consuming.
Due to its specificity, observations are limited to each community and absolute task scores might not be comparable across communities.
A study following this approach is Wefers et al. (2023) who investigated how cultural variations in parenting styles modulated infants' responses to disruptions in social interactions.
While studies in the Global North often apply the Still-Face Paradigm to assess infants' reactions to unresponsive partners, Wefers et al. (2023) reasoned that this paradigm might not capture infants' everyday interaction routines in communities with proximal (\emph{i.e.,} emphasis on body stimulation) parenting styles.
By developing the novel No-Touch Paradigm, they found that indeed infants' responses to unresponsive partners were modulated by the cultural context in which they grew up: Kichwa infants from rural Ecuador showed stronger reactions to unresponsive partners in the No-Touch Paradigm compared to the Still-Face Paradigm, while reactions of urban German infants differed less in both paradigms.

At the other extreme, researchers use the same standardized procedure across diverse communities, potentially providing a simple translation or modification of stimuli to ensure they are culturally appropriate (termed ``adoption'' and ``adaptation'', respectively Waschl \& Chen (2022)).
This approach is less sensitive to each community's unique characteristics but renders quantitative comparisons of data more feasible.
An example following this approach is the Multilingual Assessment Instrument for Narratives {[}MAIN; Gagarina et al. (2012){]}, which assesses narrative abilities in mono- and multilingual children.
Extensive piloting and adaptation of MAIN materials ensured that the instrument is culturally appropriate, robust and suitable for cross-linguistic comparisons (Gagarina et al., 2012), and new and revised language versions are continuously added to the MAIN database (Gagarina \& Lindgren, 2020).

The present paper aims to describe the development and psychometric properties of a standardized social cognition task that can be adapted to diverse communities.
Our task focuses on one of the most fundamental social-cognitive abilities: gaze following, that is, the ability to identify the attentional focus of another agent.
Gaze following develops early in infancy (Del Bianco et al., 2019; Tang et al., 2024) and contributes to social learning, communication, and collaboration (Bohn \& Köymen, 2018; Hernik \& Broesch, 2019; Shepherd, 2010; Tomasello et al., 2007).
While the question how social-environmental and cultural factors impact gaze following was recently posed as one of the big open questions in gaze following research (Astor \& Gredebäck, 2022), studies focusing on cultural variations of gaze following are rare.
Callaghan et al. (2011) investigated gaze following behind barriers in 12- and 17-month-olds from rural Canada (n = 35), Peru (n = 38) and India (n = 65). In their setup, an agent sat next to a wall or container and looked at a toy behind this barrier (experimental condition) or a sticker in front of it (control condition). The researchers then assessed whether and in which conditions the children crawled towards/around the barriers to follow the agent's gaze. While the absolute crawling rates differed across communities, children in all three communities crawled more often to gain visual access when the agent looked at an object behind the barrier compared to in front of it.
Hernik and Broesch (2019) studied 22 infants between 5 to 7 months of age from Vanuatu and used an eye-tracking procedure displaying a local actor looking at one of two objects.
Even though face-to-face interactions are less common in interactions between caregivers and children in Vanuatu than in Western communities, the result patterns of gaze following in Ni-Vanuatu infants resembled those of their Western counterparts: infants from Vanuatu followed the agent's gaze to the target object only when preceded by infant-directed, and not adult-directed, speech.
While these two studies point towards a potential cross-cultural stability of gaze following,
the lack of psychometrically evaluated tasks and the small number of communities studied limit the generalizability of these findings.

The task presented here aims to tackle these issues and builds upon a previously established gaze-following task called `TANGO' (Task for Assessing iNdividual differences in Gaze understanding - Open) by Prein et al. (2023).
The TANGO measures how precisely participants locate an agent's attentional focus.
It reliably measured individual differences in a German child sample and an English-speaking remote adult sample (Prein et al., 2023).
As we cannot claim a task's generalizability and reliability based on mono-cultural samples, we need to assess the TANGO's psychometric properties in a larger cross-cultural sample.
This paper showcases the TANGO--CC (TANGO -- Cross-Cultural), a standardized gaze following task that has been adapted to 13 languages and even more communities, and evaluates its psychometric properties by leveraging a large and diverse data set of 2.5- to 11-year-olds from 17 different communities on five continents (Bohn et al., 2024).
We describe the task's development and provide a tutorial for the open-source website (\url{https://ccp-odc.eva.mpg.de/tango-cc/}).

@@

The TANGO-CC was implemented in Leipzig, Germany, and thoroughly assessed in terms of reliability and validity (Prein et al., 2023).
During this process, the cross-cultural adaptation of the task was prepared within a team of cross-cultural psychologists and cognitive scientists.
In this paper, we assess the TANGO--CC's measurement quality (i.e., variability and reliability) across 17 diverse communities by analyzing the data set from Bohn et al. (2024).
In the following, we describe the different steps in detail.

@@

We created a public OSF page (\url{https://doi.org/10.17605/OSF.IO/P2EGU}) where we plan to collect data sets that used the TANGO-CC.
Researchers who have collected data using the TANGO--CC can share their data with the community by contacting the first author of this paper or visiting this OSF repository.

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{cross-cultural psychology, social cognition, gaze following, individual differences, reliability\newline\indent Word count: XXX}
\usepackage{lineno}

@@

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Measuring variation in gaze following across communities, ages, and individuals --- a showcase of the TANGO--CC},
  pdfauthor={Julia Christin Prein (ORCID: 0000-0002-3154-6167)1,2, Florian M. Bednarski (ORCID: 0000-0003-4384-4791)3, Ardain Dzabatou4, Michael C. Frank (ORCID: 0000-0002-7551-4378)5, Annette M. E. Henderson (ORCID: 0000-0003-4384-4791)3, Josefine Kalbitz2, Patricia Kanngiesser (ORCID:0000-0003-1068-3725)6, Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733)7, Bahar Köymen (ORCID: 0000-0001-5126-8240)8, Maira V. Manrique-Hernandez2, Shirley Magazi (ORCID: 0009-0006-0479-9800)9, Lizbeth Mújica-Manrique2, Julia Ohlendorf2, Damilola Olaoba2, Wesley R. Pieters (ORCID:0000-0002-6152-249X)9, Sarah Pope-Caldwell2, Umay Sen (ORCID: 0000-0001-9488-0851)10, Katie Slocombe (ORCID: 0000-0002-7310-1887)11, Robert Z. Sparks (ORCID: 0000-0001-7545-0522)5, Roman Stengelin (ORCID: 0000-0003-2212-4613)2,9, Jahnavi Sunderarajan2, Kirsten Sutherland2, Florence Tusiime12, Wilson Vieira (ORCID: 0009-0001-9400-6328)2, Zhen Zhang (ORCID: 0000-0001-9300-0920)13, Yufei Zong (ORCID: 0009-0000-5012-0244)13, Daniel B. M. Haun (ORCID: 0000-0002-3262-645X)2,+, \& Manuel Bohn (ORCID: 0000-0001-6006-1348)1,2,+},
  pdflang={en-EN},
  pdfkeywords={cross-cultural psychology, social cognition, gaze following, individual differences, reliability},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Measuring variation in gaze following across communities, ages, and individuals --- a showcase of the TANGO--CC}
\author{Julia Christin Prein (ORCID: 0000-0002-3154-6167)\textsuperscript{1,2}, Florian M. Bednarski (ORCID: 0000-0003-4384-4791)\textsuperscript{3}, Ardain Dzabatou\textsuperscript{4}, Michael C. Frank (ORCID: 0000-0002-7551-4378)\textsuperscript{5}, Annette M. E. Henderson (ORCID: 0000-0003-4384-4791)\textsuperscript{3}, Josefine Kalbitz\textsuperscript{2}, Patricia Kanngiesser (ORCID:0000-0003-1068-3725)\textsuperscript{6}, Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733)\textsuperscript{7}, Bahar Köymen (ORCID: 0000-0001-5126-8240)\textsuperscript{8}, Maira V. Manrique-Hernandez\textsuperscript{2}, Shirley Magazi (ORCID: 0009-0006-0479-9800)\textsuperscript{9}, Lizbeth Mújica-Manrique\textsuperscript{2}, Julia Ohlendorf\textsuperscript{2}, Damilola Olaoba\textsuperscript{2}, Wesley R. Pieters (ORCID:0000-0002-6152-249X)\textsuperscript{9}, Sarah Pope-Caldwell\textsuperscript{2}, Umay Sen (ORCID: 0000-0001-9488-0851)\textsuperscript{10}, Katie Slocombe (ORCID: 0000-0002-7310-1887)\textsuperscript{11}, Robert Z. Sparks (ORCID: 0000-0001-7545-0522)\textsuperscript{5}, Roman Stengelin (ORCID: 0000-0003-2212-4613)\textsuperscript{2,9}, Jahnavi Sunderarajan\textsuperscript{2}, Kirsten Sutherland\textsuperscript{2}, Florence Tusiime\textsuperscript{12}, Wilson Vieira (ORCID: 0009-0001-9400-6328)\textsuperscript{2}, Zhen Zhang (ORCID: 0000-0001-9300-0920)\textsuperscript{13}, Yufei Zong (ORCID: 0009-0000-5012-0244)\textsuperscript{13}, Daniel B. M. Haun (ORCID: 0000-0002-3262-645X)\textsuperscript{2,+}, \& Manuel Bohn (ORCID: 0000-0001-6006-1348)\textsuperscript{1,2,+}}
\date{}

@@

The authors made the following contributions. Julia Christin Prein (ORCID: 0000-0002-3154-6167): Conceptualization, Formal Analysis, Methodology, Project administration, Resources, Software, Visualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Florian M. Bednarski (ORCID: 0000-0003-4384-4791): Methodology, Resources, Writing - Review \& Editing; Ardain Dzabatou: Methodology, Resources, Writing - Review \& Editing; Michael C. Frank (ORCID: 0000-0002-7551-4378): Methodology, Resources, Writing - Review \& Editing; Annette M. E. Henderson (ORCID: 0000-0003-4384-4791): Methodology, Resources, Writing - Review \& Editing; Josefine Kalbitz: Methodology, Resources, Writing - Review \& Editing; Patricia Kanngiesser (ORCID:0000-0003-1068-3725): Methodology, Resources, Writing - Review \& Editing; Dilara Keşşafoğlu (ORCID: 0000-0002-7356-0733): Methodology, Resources, Writing - Review \& Editing; Bahar Köymen (ORCID: 0000-0001-5126-8240): Methodology, Resources, Writing - Review \& Editing; Maira V. Manrique-Hernandez: Methodology, Resources, Writing - Review \& Editing; Shirley Magazi (ORCID: 0009-0006-0479-9800): Methodology, Resources, Writing - Review \& Editing; Lizbeth Mújica-Manrique: Methodology, Resources, Writing - Review \& Editing; Julia Ohlendorf: Methodology, Resources, Writing - Review \& Editing; Damilola Olaoba: Methodology, Resources, Writing - Review \& Editing; Wesley R. Pieters (ORCID:0000-0002-6152-249X): Methodology, Resources, Writing - Review \& Editing; Sarah Pope-Caldwell: Methodology, Resources, Writing - Review \& Editing; Umay Sen (ORCID: 0000-0001-9488-0851): Methodology, Resources, Writing - Review \& Editing; Katie Slocombe (ORCID: 0000-0002-7310-1887): Methodology, Resources, Writing - Review \& Editing; Robert Z. Sparks (ORCID: 0000-0001-7545-0522): Methodology, Resources, Writing - Review \& Editing; Roman Stengelin (ORCID: 0000-0003-2212-4613): Conceptualization, Methodology, Resources, Writing - Review \& Editing; Jahnavi Sunderarajan: Methodology, Resources, Writing - Review \& Editing; Kirsten Sutherland: Methodology, Resources, Writing - Review \& Editing; Florence Tusiime: Methodology, Resources, Writing - Review \& Editing; Wilson Vieira (ORCID: 0009-0001-9400-6328): Methodology, Resources, Writing - Review \& Editing; Zhen Zhang (ORCID: 0000-0001-9300-0920): Methodology, Resources, Writing - Review \& Editing; Yufei Zong (ORCID: 0009-0000-5012-0244): Methodology, Resources, Writing - Review \& Editing; Daniel B. M. Haun (ORCID: 0000-0002-3262-645X): Conceptualization, Funding acquisition, Methodology, Writing - Review \& Editing; Manuel Bohn (ORCID: 0000-0001-6006-1348): Conceptualization, Funding acquisition, Methodology, Project administration, Supervision, Writing - Review \& Editing.

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute of Psychology in Education, Leuphana University Lüneburg, Germany\\\textsuperscript{2} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Germany\\\textsuperscript{3} School of Psychology, University of Auckland, New Zealand\\\textsuperscript{4} Université Marien Ngouabi, Republic of the Congo\\\textsuperscript{5} Department of Psychology, Stanford University, USA\\\textsuperscript{6} School of Psychology, University of Plymouth, UK\\\textsuperscript{7} Department of Psychology, Koç University, Türkiye\\\textsuperscript{8} Division of Psychology, Communication, and Human Neuroscience, University of Manchester, UK\\\textsuperscript{9} Department of Psychology and Social Work, University of Namibia, Namibia\\\textsuperscript{10} Department of Psychology, Developmental Psychology, Uppsala University, Sweden\\\textsuperscript{11} Department of Psychology, University of York, UK\\\textsuperscript{12} Budongo Conservation Field Station, Uganda\\\textsuperscript{13} CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences, China\\\textsuperscript{+} joint last author}

\abstract{%
Cross-cultural studies are crucial for investigating the cultural variability and universality of cognitive developmental processes. However, cross-cultural assessment tools in cognition across languages and communities are limited. This paper describes a gaze following task designed to measure basic social cognition across individuals, ages, and communities (TANGO--CC). The task was developed and psychometrically assessed in one cultural setting and, with input of local collaborators, adapted for cross-cultural data collection. Minimal language demands and the web-app implementation allow fast and easy contextual adaptations to each community. The TANGO--CC captures individual- and community-level variation and shows good internal consistency in a data set from 2.5- to 11-year-old children from 17 diverse communities. Within-community variation outweighed between-community variation. We provide an open-source website for researchers to customize and use the task (\url{https://ccp-odc.eva.mpg.de/tango-cc}). The TANGO--CC can be used to assess basic social cognition in diverse communities and provides a roadmap for researching community-level and individual-level differences across cultures.
}

@@

For decades, researchers have advocated for more diverse samples in psychological research and cautioned against relying solely on convenience samples from the Global North (Arnett, 2008; Henrich et al., 2010; Lillard, 1998).
Despite numerous calls for change, the samples reported in major psychology journals still lack diversity (Apicella et al., 2020; Gutchess \& Rajaram, 2023; Thalmayer et al., 2021).
This hinders progress in theory building and testing: we cannot draw inferences about universal and variable aspects of the human cognitive system from data collected exclusively in one single community (Krys et al., 2024).
While this sampling bias is often discussed within adult psychology, it is equally relevant to developmental psychology (Nielsen et al., 2017).
Early experiences shape the way children think about and interact with the world and an ontogenetic perspective is needed to explore the foundational aspects of human behavioral diversity (Amir \& McAuliffe, 2020; Broesch et al., 2023; Liebal \& Haun, 2018; Torréns et al., 2023).

There are numerous challenges with collecting cross-cultural, developmental data (Amir \& McAuliffe, 2020; Broesch et al., 2023).
Cross-cultural studies need reliable and valid measures to capture variation between communities and/or individuals systematically.
Even though this applies to all areas of cognitive development, we focus on social cognition in this paper.

Social cognition refers to how an individual processes information in social situations which allows them to understand and predict others' behavior (Adolphs, 1999; Decety, 2020; Frith \& Frith, 2007; Zeigler-Hill et al., 2015).
If, in theory, stimuli used in social cognition tasks should relate to people's everyday experiences, then tasks themselves should be tuned to the features of specific communities.
Indeed, task performance can be diminished when stimuli do not reflect the characteristics of the participants' communities (Peña, 2007).
For example, Elfenbein and Ambady (2002) found better emotion recognition for members of the same national, ethnic, or regional group.
Selcuk et al. (2023) concluded that children often attribute mental states more accurately and more frequently to individuals from the same community.

From a psychometric perspective, the situation looks dire. Studies on social cognition with US-American and European samples rarely report psychometric information (for a review, see Beaudoin et al., 2020), and the picture further deteriorates when we look at cross-cultural social cognition tasks (Bourdage et al., 2023; Hajdúk et al., 2020; Waschl \& Chen, 2022).
Thus, it is already challenging to find reliable and valid tasks that have measurement sensitivity to detect individual differences within one community, let alone tasks that do so across different communities.
In this paper, we describe the construction and psychometric evaluation of a cross-cultural measure of basic social cognition (gaze following) in children as a concrete example of how to address this problem.

The approaches that researchers can take to collect cross-cultural data lie on a continuum: the decision for a specific method partly depends on whether researchers aim to increase the \emph{depth} (culture specificity) or \emph{breadth} (standardization across multiple communities) of their work (Amir \& McAuliffe, 2020).
At one extreme, researchers translate the psychological construct into a separate design or task for each community (termed ``assembly''; He and Vijver (2012), Waschl and Chen (2022)).
While this approach allows greater flexibility and sensitivity to cultural differences, it might not be feasible to study a multitude of communities as it becomes too demanding and time-consuming.
Furthermore, the results are limited to each community and absolute task scores might not be comparable across communities.
A study following this approach is Wefers et al. (2023) who investigated how cultural variations in parenting styles modulated infants' responses to disruptions in social interactions.
While studies in the Global North often apply the Still-Face Paradigm to assess infants' reactions to unresponsive partners, Wefers et al. (2023) reasoned that this paradigm might not capture infants' everyday interaction routines in communities with proximal (\emph{i.e.,} emphasis on body stimulation) parenting styles.
By developing the novel No-Touch Paradigm, they found that indeed infants' responses to unresponsive partners were modulated by the cultural context in which they grew up: Kichwa infants from rural Ecuador showed stronger reactions to unresponsive partners in the No-Touch Paradigm compared to the Still-Face Paradigm, while reactions of urban German infants differed less in both paradigms.

At the other extreme, researchers use the same standardized procedure across diverse communities, potentially providing a simple translation or modification of stimuli to ensure they are culturally appropriate (termed ``adoption'' and ``adaptation'', respectively; Waschl \& Chen (2022)).
This approach is less sensitive to each community's unique characteristics but renders quantitative comparisons of data more feasible.
An example following this approach is the Multilingual Assessment Instrument for Narratives (MAIN; (Gagarina et al., 2012)), which assesses narrative abilities in mono- and multilingual children.
Extensive piloting and adaptation of MAIN materials ensured that the instrument is culturally appropriate, robust, and suitable for cross-linguistic comparisons (Gagarina et al., 2012), and new and revised language versions are continuously added to the MAIN database (Gagarina \& Lindgren, 2020).

The present paper aims to describe the development and psychometric properties of a social cognition task that can be adapted to diverse communities.
On the continuum described above, our task lies more toward standardized approaches but allows for some customization of the stimuli to each local community.
The task focuses on one of the most fundamental social-cognitive abilities: gaze following, that is, the ability to identify the attentional focus of another agent.
Gaze following develops early in infancy (Del Bianco et al., 2019; Tang et al., 2024) and contributes to social learning, communication, and collaboration (Bohn \& Köymen, 2018; Hernik \& Broesch, 2019; Shepherd, 2010; Tomasello et al., 2007).
While the question of how social-environmental and cultural factors impact gaze following was recently posed as one of the big open questions in gaze following research (Astor \& Gredebäck, 2022), studies focusing on cultural variations of gaze following are rare.
Callaghan et al. (2011) investigated gaze following behind barriers in 12- and 17-month-olds from rural Canada (n = 35), Peru (n = 38), and India (n = 65).
In their setup, an agent looked at a toy behind (experimental condition) or a sticker in front of (control condition) a barrier, and children's crawling toward the barrier to follow the agent's gaze was assessed.
While the absolute crawling rates differed across communities, children in all three communities crawled more often to gain visual access when the agent looked at an object behind the barrier than in front of it.
Hernik and Broesch (2019) studied 22 infants between 5 to 7 months of age from Vanuatu and used an eye-tracking procedure displaying a local actor looking at one of two objects.
Even though face-to-face interactions are less common in parent-child interactions in Vanuatu than in Western communities, the result patterns of gaze following in Ni-Vanuatu infants resembled those of their Western counterparts: infants from Vanuatu followed the agent's gaze to the target object only when preceded by infant-directed, and not adult-directed, speech.
While these two studies point towards potential cross-cultural stability of gaze following, the lack of psychometrically evaluated tasks and the small number of communities studied limit the generalizability of these findings and -- more importantly -- does not allow for studying individual-differences.
A more comprehensive cross-cultural study on gaze following was recently conducted by Bohn et al. (2024). The researchers tested the universality of gaze following by studying 17 different communities on five continents and found evidence for a similar processing mechanism across communities.

The task presented in this manuscript was developed for the study by Bohn et al. (2024) and is based on a previously established gaze-following task called `TANGO' (Task for Assessing iNdividual differences in Gaze understanding - Open) by Prein et al. (2023).
The TANGO measures how precisely participants locate an agent's attentional focus.
It reliably measured individual differences in a German child sample and an English-speaking remote adult sample (Prein et al., 2023).
However, we cannot claim the task's generalizability and reliability based on a mono-cultural sample.
This paper showcases the TANGO--CC (TANGO -- Cross-Cultural), a standardized gaze following task that has been adapted to 13 languages and even more communities, and evaluates its psychometric properties by leveraging a large and diverse data set of 2.5- to 11-year-olds from 17 diverse communities (Bohn et al., 2024).
We describe the task's development and provide a tutorial for the open-source website (\url{https://ccp-odc.eva.mpg.de/tango-cc/}).

@@

The TANGO-CC was implemented in Leipzig, Germany, and thoroughly assessed in terms of reliability and validity (Prein et al., 2023).
During this process, the cross-cultural adaptation of the task was prepared by a team of cross-cultural psychologists and cognitive scientists.
In this paper, we assess the TANGO--CC's measurement quality (\emph{i.e.,} variability and reliability) across 17 diverse communities by analyzing the data set from Bohn et al. (2024).
In the following, we describe the different steps in detail.

@@

We created a public OSF page (\url{https://doi.org/10.17605/OSF.IO/P2EGU}) on which we plan to collect data sets that used the TANGO-CC.
Researchers who have collected data using the TANGO--CC can share their data with the community by contacting the first author of this paper or visiting the OSF repository.
